\chapter{Chapter 4}
\section{Introduction}
In this Chapter, we still focus on the DCA data pre-processing phase. We   propose   novel approaches to more improve  the standard DCA data pre-processing task. This is achieved through the use of Fuzzy Rough Set Theory (FRST) \cite{FRST}. The proposed algorithms are seen as extensions to the   rough  set algorithms which were previously presented in Chapter 3.     

The rest of this Chapter is organized as follows: Section 4.2 deals with the motivation behind the use of  FRST for data pre-processing. Our developed DCA variants are explained in details in Sections 4.3, 4.4 and 4.5. A comparison of our proposed algorithms is presented in Section 4.6.
\section{Why Adopting Fuzzy-Rough Sets for Data Pre-processing?}
....


\section{Conclusion}
Throughout this Chapter, we focused our work on using fuzzy rough set theory for the DCA data pre-processing phase. We have developed three fuzzy-rough DCAs  based on different methodologies for the feature selection and signal categorization processes. These methods were compared  and the appropriate observations were noted.  

Up to now, we have made a deep investigation of the DCA data pre-processing phase.  We have proposed adequate solutions to build a solid data pre-processing module. While focusing on the rest DCA algorithmic steps, more investigations have to de done. To begin with and in the next Chapter, we will   focus on solving the DCA limitation as it is sensitive to the input class data order.




